---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Shen Liu"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = Date, y = Cases_Total)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```
```{r}
covid_data_count |> 
  filter(race == "Asian") |>
  ggplot(aes(x = Cases, y = Deaths, color = state)) + 
  geom_point(alpha = 0.8, size = 1) +
  geom_smooth() + 
  scale_x_continuous(breaks = seq(0, 3500000, by = 10000)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  labs(
    title = "Covid Cases And Death for Asian",
    legend = "state"
  )
```

1. Write code for a plot and describe what you observe?

   I can see the number of cases and deaths in different states, especially state CA has the most cases and deaths. In addition, it is not hard to see the relation between cases and deaths.
   
2. Are there any conclusions you can draw?

   In all states, as Covid cases for Asian increases, deaths also increases.
   
3. What were you not able to do due to not having the R knowledge?

   To make the figure look not so crowd and make the color legend easier to distinguish.
   
4. What other data would be useful to better understand this data?

   The cases and deaths for other famous diseases other than Covid. Then by comparing the data, we can see how the situation and the deaths rate the Covid had. By doing so, we can understand Covid better.
